---
title: "Randomized and Quasi-Randomized 'neural' networks for supervised learning
  and multivariate time series forecasting"
author: "T. Moudiki"
date: "2023-10-17"
output:
  pdf_document: default
  html_document:
    df_print: paged
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Version `v0.14.0` of nnetsauce is now available for R (hopefully a rapid installation) and Python on GitHub (https://github.com/Techtonique/nnetsauce), PyPI (https://pypi.org/project/nnetsauce/) and conda (https://anaconda.org/conda-forge/nnetsauce). It's been mainly tested on Linux and macOS. For Windows users, you can try to install it of course, but if it doesn't work, please use  WSL2 (https://learn.microsoft.com/en-us/windows/wsl/install).

**Contents**

- 1 - R News
- 1 - 1 - Elastic Net with Kernel Density simulation of residuals (strong hypothesis)
- 1 - 2 - Bayesian forecasting
- 2 - colored graphics for `Python` class `MTS` 

# 1 - R News

Update and align as much as possible Python version with `R` version after a long hiatus (new plotting function for multivariate time series (`MTS`), `plot.MTS`, is not [`S3`](https://cran.r-project.org/doc/manuals/R-exts.html#Registering-S3-methods) yet, it’s complicated)


```{r "chunk-2-packages", echo=TRUE, results='hide'}


utils::install.packages(c("remotes", "fpp", "reticulate"))
remotes::install_github("Techtonique/nnetsauce/R-package")


```

```{r "chunk-3-load-packages", echo=TRUE, results='hide'}


library(fpp)
library(nnetsauce)


```

# 1 - 1 - Elastic Net with Kernel Density simulation of residuals (strong hypothesis)

```{r "chunk-4-enet", echo=TRUE, results='hide'}

obj <- nnetsauce::sklearn$linear_model$ElasticNet()
obj2 <- nnetsauce::MTS(obj, 
                       start_input = start(fpp::vn), 
                       frequency_input = frequency(fpp::vn),
                       kernel = "gaussian", replications = 100L)
X <- data.frame(fpp::vn)
obj2$fit(X)
obj2$predict(h = 10L)
typeof(obj2)
```

```{r "chunk-5-plot-enet-simulations"}


par(mfrow=c(2, 2))
plot.MTS(obj2, selected_series = "Sydney")
plot.MTS(obj2, selected_series = "Melbourne")
plot.MTS(obj2, selected_series = "NSW")
plot.MTS(obj2, selected_series = "BrisbaneGC")


```

# 1 - 2 - Bayesian forecasting

```{r "chunk-6-bayesian-forecasting", echo=TRUE, results='hide'}


obj <- nnetsauce::sklearn$linear_model$BayesianRidge()
obj2 <- nnetsauce::MTS(obj,
                       start_input = start(fpp::vn), 
                       frequency_input = frequency(fpp::vn))
X <- data.frame(fpp::vn)
obj2$fit(X)
obj2$predict(h = 10L, return_std = TRUE)


```

```{r "chunk-7-plot-bayesian"}


par(mfrow=c(2, 2))
nnetsauce::plot.MTS(obj2, selected_series = "Sydney")
nnetsauce::plot.MTS(obj2, selected_series = "Melbourne")
nnetsauce::plot.MTS(obj2, selected_series = "NSW")
nnetsauce::plot.MTS(obj2, selected_series = "BrisbaneGC")


```


# 2 - colored graphics for `Python` class `MTS` 

```{r "chunk-8-install-nnetsauce-py", echo=TRUE, results='hide'}


reticulate::py_install("nnetsauce") # or pip install nnetsauce


```

```{python "chunk-9-ns-py", echo=TRUE, results='hide'}


import nnetsauce as ns
import numpy as np
import pandas as pd
from sklearn.linear_model import Ridge, BayesianRidge
from sklearn.ensemble import RandomForestRegressor
from time import time

url = "https://raw.githubusercontent.com/thierrymoudiki/mts-data/master/heater-ice-cream/ice_cream_vs_heater.csv"

df = pd.read_csv(url)

# ice cream vs heater (I don't own the copyright)
df.set_index('Month', inplace=True)
df.index.rename('date')

df = df.pct_change().dropna()

idx_train = int(df.shape[0]*0.8)
idx_end = df.shape[0]
df_train = df.iloc[0:idx_train,]

regr3 = Ridge()
obj_MTS3 = ns.MTS(regr3, lags = 5, n_hidden_features=7, #IRL, must be tuned
                  replications=50, kernel='gaussian',
                  seed=24, verbose = 1)
start = time()
obj_MTS3.fit(df_train)
print(f"Elapsed {time()-start} s")

obj_MTS3.predict(h = 15)


```

```{python "chunk-10-plot-ns-py"}


obj_MTS3.plot("heater")
obj_MTS3.plot("ice cream")


```

```{r}


sessionInfo()


```

