---
title: "nnetsauce for R: RandomBagClassifier on iris dataset"
output:
  html_document:
    df_print: paged
---


## Import packages

The model presented in this notebook is a [bootstrap aggregating model](https://en.wikipedia.org/wiki/Bootstrap_aggregating) built on quasi-randomized networks. 

We start by __importing__ [nnetsauce](https://thierrymoudiki.github.io/software/nnetsauce/) from GitHub, by using `R` package `devtools`.

```{r}
library(devtools)
devtools::install_github("thierrymoudiki/nnetsauce/R-package")
library(nnetsauce)
```

## Import data  

`iris` dataset from `R` package `datasets` is used in this notebook. The following chunk creates a __target variable__ `y` to be explained (class of a flower), and a set of __explanatory variables__ `X`.

```{r}
library(datasets)
X <- as.matrix(iris[, 1:4])
y <- as.integer(iris[, 5]) - 1L
```

## Create training set and test set

`iris` dataset is randomly splitted into a training set and a test set. The test set serves for measuring model performance on unseen data. 

```{r}
n <- dim(X)[1]
p <- dim(X)[2]

set.seed(213)
train_index <- sample(x = 1:n, size = floor(0.8*n), replace = TRUE) 
test_index <- -train_index

X_train <- as.matrix(iris[train_index, 1:4])
y_train <- as.integer(iris[train_index, 5]) - 1L
X_test <- as.matrix(iris[test_index, 1:4])
y_test <- as.integer(iris[test_index, 5]) - 1L
```

## Model fitting

Create model `RandomBagClassifier` and adjust it to the training set. Notice the difference with Python here: a `$` is used instead of a `.` for accessing model attributes and invoking methods. A decision tree model is used as _base learner_ for the `RandomBagClassifier`, but any model having methods `fit` and `predict` could be used:

```{r}
obj <- sklearn$tree$DecisionTreeClassifier()
obj2 <- RandomBagClassifier(obj, n_estimators = 250L, 
                            n_hidden_features = 5L,
                            n_clusters = 3L,
                            type_clust = "gmm")
obj2$fit(X_train, y_train)
```

## Score model on test set 

Obtain model __accuracy__ on test set: 

```{r}
print(obj2$score(X_test, y_test))
```


